Manuscript title here

### 2024-10-30 manuscript.Rmd

```{=html}
<!-- Explain the scientific background and rationale for the
investigation being reported. End by stating the aim or specific
objectives, including any prespecified hypotheses. The introduction
should not be longer than 1-1.5 pages, typically 4-5 paragraphs, each
6-8 lines long. Support every statement with a citation -->
```
You can cite document here like this [@exampleKey9999]. Open the file bibliography.bib to learn more.

Trauma is a major global public health concern. It causes over four milion death and affects hundreds of millions each year, among those younger populations are the most affected [@noauthor_injuries_nodate]. The initial management of trauma patients once they reach hospital is very time sensitive and error prone [@mackersie_pitfalls_2010] [@teixeira_preventable_2007][@ivatury_patient_2008], and shock is the most common potentially preventable death within the first 24h of injury[@berry_shock_2015]. It is also the second major cause of early mortality in trauma patients [@kauvar_impact_2006], and patients in shock have a higher mortality rate than those not[@vang_shock_2022].

@@

@@

>>>>

```{=html}
<!-- Explain the scientific background and rationale for the
investigation being reported. End by stating the aim or specific
objectives, including any prespecified hypotheses. The introduction
should not be longer than 1-1.5 pages, typically 4-5 paragraphs, each
6-8 lines long. Support every statement with a citation -->
```
Trauma is a major global public health concern. It causes over four milion death and affects hundreds of millions each year, among those younger populations are the most affected [@noauthor_injuries_nodate]. The initial management of trauma patients once they reach hospital is very time sensitive and error prone [@mackersie_pitfalls_2010] [@teixeira_preventable_2007][@ivatury_patient_2008], and shock is the most common potentially preventable death within the first 24h of injury[@berry_shock_2015]. It is also the second major cause of early mortality in trauma patients [@kauvar_impact_2006], and patients in shock have a higher mortality rate than those not[@vang_shock_2022].

@@

There were a total of `r nrow(merged.data)` patients in the trauma registry. Out of these, `r nrow(study.sample)` patients had been reviewed for the presence of opportunities for improvement. After exluding patients younger than 15 and/or were dead on arrival, `r nrow(study.sample)` patients remained. A total of X patients were finally excluded due to missing data, leaving us with Y patients for the final analysis.

@@

Sample characteristics are presented in Table \@ref(tab:sample-characteristics). A total of `r ofi` patients had at least one opportunity for improvement. The median age was `r age`. Most patients were male `r gender`.

```{r sample-characteristics, echo=FALSE}
sample.characteristics.table
```
